An investigation of times that a lack in good physical security practices led to a cyber security issue

### 2024-02-13 Paper/Paper.tex
More work

\documentclass[acmsmall]{acmart}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers

@@

\acmYear{2024}
\acmDOI{cybersecurity.tomcruise}
\acmJournal{TISSEC}
\acmVolume{420}
\acmNumber{69}
% \acmArticle{3.14}
\acmMonth{1}

@@

\begin{document}

% \title{Historic Cybersecurity Breaches Caused by a Lack of Physical Security}
\title{An investigation of times that a lack in good physical security practices led to a cyber security issue}

@@

\maketitle
\fancyfoot{}
\thispagestyle{empty}

@@

Ultimately, physical security can be just as important and just as in-depth
as cybersecurity.

@@

\section{Method of Attack}
It is believed that the attacker was able to remotely access the system through
TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
in the water from 100 parts per million to 11,100 parts per million.

\section{Now You See Me 2}
While not a real-life example, the movie Now You See Me 2 \cite{NowYouSeeMe2} presents
a potential example of a physical security breach. In the movie, the main characters
are able to breach a company's phone presentation by disguising as server maintenance,
quickly convincing security that the original server maintainer was crazy, and
installing a device that would allow them to control the presentation.

\subsection{Attack}
While very entertaining, the attack in the movie is not entirely realistic. Quick uniform
changes and pretending that you belong was presented to seem entirely plausible. Regardless,
the important parts of the attack were that the server room was easily accessible by all staff
with only one layer of security. The single layer was a wired door that was left open
by the original server maintainer.

Once the main character was in the server room disguised, he took a portable camera that could
immediately print out a picture and pretended that it was "picture day" for the maintainer.
The maintainer was not fooled by the lies, however, he was too confused and insisted that the
character should not be there. Regardless, The main character printed out the picture and
placed it on a badge for a mental facility.

Upon calling for security, the main character was able to convince the security that the
maintainer was crazy and that he was the real maintainer. The main character was then able
to install a device that would allow him to control the presentation.

\subsection{Analysis}
This attack was successful because of a lack of physical security. The server room was
easily accessible by all staff and only had a single layer of security. The maintainer
also left the door open, allowing the main character to easily enter the room.
With no physical keycard, identification, or other security, the main character was
able to easily enter the room.

\subsection{Mitigation}
Ideally, the server room would have had a physical keycard, identification, or other
security that would have prevented the main character from entering the room. The
maintainer should have also locked the door behind him, preventing the main character
from entering the room. Lastly, ideally the security guards would have been trained
to be aware of social engineering and to not be easily convinced by lies.

\section{Mission Impossible \texorpdfstring{\cite{missionimpossible}}{}}
A more realistic example of a physical security breach is in the movie
Mission Impossible. In the movie, Ethan Hunt (played by Tom Cruise) is tasked
with stealing the NOC list from a CIA building. The NOC list is a list of all
CIA agents that are currently undercover. The CIA building is heavily guarded
and has many layers of security.

\subsection{Attack}
The move shows the many physical layers of security that the CIA
building has. The building has a security guard, a security camera, a keycard
reader, and a physical key. Access to the NOC list is also restricted to only
the physical computer that the NOC list is on. The server room employs many
measures and monitors to prevent unauthorized access.

Specifically, the server room has pressure-sensitive floors, a temperature monitor,
sound sensor, and lasers above the ventilation system. All of these measures are disabled
while an authorized person is in the room, and re-enabled when they leave.

Ethan Hunt goes through the ventilation system, uses a mirror to reflect the
lasers, and is slowly lowered to the floor by a wire. He then hacks into the
computer and steals the NOC list.

\subsection{Analysis}
Here we can see that the CIA building has many layers of physical security.
Despite all of these layers, Ethan Hunt was still able to breach the security.
Unfortunately, the CIA building failed to account for plot armor, which is
a classic mistake in the field of cybersecurity.

\subsection{Mitigation}
Realistically, the CIA building should have had a more secure ventilation system;
we see that the team was able to get into the ventilation system (and the building itself)
by disguising as firefighers. The CIA did not have proper protocols or procedures
for fire alarms or drills, which allowed the team to easily enter the building.

Additionally, requiring an authorized person to be in the room to access the
computer would be a good requirement.

@@

Ensuring that all employees are trained to be aware of physical security and the dangers
of social engineering is important. Additionally, ensuring that all employees are trained
to be aware of the dangers of plugging in unauthorized devices is important. Having properly
defined protocols and procedures for unlikely events is also important.
Companies should internally test their security- GitLab for example similarly has a
"Red Team" that is tasked with trying to hack GitLab \cite{GitLab}.

\begin{acks}
  I would like to thank Google for their Plasma Globe attack, and the creators of
  Mission Impossible for their interesting portrayal of physical security.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib}
\end{document}
\endinput

>>>>

\documentclass[acmsmall]{acmart}
\usepackage{fancyhdr}

\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column

@@

\acmYear{2024}
\acmDOI{cybersecurity.tomcruise}
\acmJournal{TISSEC}
\acmVolume{420}
\acmNumber{69}
\acmMonth{1}

@@

\begin{document}
\title{An investigation of times that a lack in good physical security practices led to a cyber security issue}

@@

\maketitle

\fancyfoot{}
\thispagestyle{empty}

@@

Ultimately, physical security is necessary to ensure proper cybersecurity.

@@

\subsection{Method of Attack}
It is believed that the attacker was able to remotely access the system (supposedly)
through TeamViewer. The attacker was able to increase the amount of sodium hydroxide (lye)
in the water from 100 parts per million to 11,100 parts per million. Thankfully,
the system's operator noticed the change and reverted it back to the normal levels.

\cite{CCNFlorida} ultimately concludes that the attack was done remotely. The
water treatment system was outdated and not kept up-to-date to proper security
standards. "Gualtieri said the water treatment facility currently uses a Google
Chrome product for remote access. The Oldsmar water treatment system is also using
the Windows 7 operating system, which was released in 2009" \cite{CCNFlorida}.

\subsection{Attack Analysis}
The allowance of remote access to Oldsmar's water treatment system was a major
security concern. A lack of proper security standards and outdated software
contributed to the attack being successful \cite{CCNFlorida}. A cyber secure-forward
culture would have ensured that any remote access was authenticated, validated,
logged, and audited.

Physical elements of a cyber secure culture could include requiring a physical
security key, VPN, or timed access to the system. The Hill \cite{HillArticle}
admits that "Unfortunately, that water treatment facility is the rule rather than
the exception. When an organization is struggling to make payroll and to keep systems
on a generation of technology created in the last decade, even the basics in cybersecurity
often are out of reach."

Ultimately a cyber secure culture needs to take into account maintenance and
upkeep of the physical systems.

\subsection{Mitigation and Response}
A follow-up article by CyberScoop \cite{CyberScoop} reveals that it may not have
been a cyber-attack at all, and that it could have been an unintentional action by an
employee.

"The FBI concluded there was nothing, no evidence of any access from the outside,
and that it was likely the same employee that was purported to be a hero for catching
it, was actually banging on his keyboard" \cite{CyberScoop}.

Even though this may not have been an actual outsider attack, the potential was certainly
still present. According to \cite{CyberScoop}, "a data leak containing the email
addresses and passwords with two domains belonging to Oldsmar surfaced days before the
breach occurred".

With a lack of proper financial resoruces, it is difficult to ensure that the
water treatment system is up-to-date and secure.

Another interesting perspective of cyber security culture is how it relates to
federal and public policy. The Biden Administration is slowly making progress
to have cyber-security requirements, and the Environmental Protection Agency released
a mandate for public water systems to "evaluate the adequacy" of any digital defenses
through sanitation surveys \cite{CyberScoopEPA}.

\section{Credit Card Skimmers}
An interesting example of a physical security breach is the use of credit card skimmers.
Credit card skimmers are devices that are placed on top of a credit card reader that
are able to read and store the information of a credit card. The skimmer is then
retrieved by the attacker and the information is used to make unauthorized purchases \cite{FBISkimming}.

While not be a direct physical security breach, the use of credit card skimmers
is directly related to cyber security, as credit card information can be viewed
as a form of digital information.

Though the mindset and knowledge of card skimming may not wholly be a part of a
cyber secure culture, being aware of the current dangers and threats is important
to a cyber secure culture. Customers, credit card companies, and businesses all
need to be aware of the dangers of credit card skimmers.

In one instance, six people were arrested and charged with using credit card skimmers
to steal over \$5 million dollars from credit unions and banks \cite{FBISkimming}.
This provides a critical reminder for the importance of physical security when it comes
to cybersecurity. No matter how secure the software of an ATM is, a credit card skimmer
can still be placed on top of it.

\subsection{The Culture of Credit Card Skimming}
While the typical scope of a security culture may be based off of a company's
policies, executives, and employees, cultures are not limited to just companies.
The cyber-secure culture of a city, state, or country can also be evaluated,
analyzed, and improved. The Federal Bureau of Investigation (FBI) has a page
dedicated to credit card skimming, and the FBI is working to educate the public
about the dangers of credit card skimming \cite{FBISkimming}.

@@

Ensuring that all employees are trained to be aware of physical security and the dangers
of social engineering is important. Additionally, ensuring that all employees are trained
to be aware of the dangers of plugging in unauthorized devices is important. Having properly
defined protocols and procedures for unlikely events is also important.
Companies should internally test their security- GitLab for example (similar to Google) has a
"Red Team" that is tasked with trying to hack GitLab \cite{GitLab}.

\bibliographystyle{unsrtnat}
\bibliography{bib}
\end{document}
\endinput
